D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-05 ootavacuous.tex
Add JMM Causality Test Cases 11-20
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Listing~\ref{lst:Causality Test Case 1}
shows causality test case 1, for which the \co{r1 == r2 == 1} result
is to be allowed.
However, the herd7 tool does not find this litmus test's cycle, presumably
because this tool does not do the deep inter-thread compiler analysis
required to find it.

@@

Listing~\ref{lst:Causality Test Case 2}
shows causality test case 2, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 3}
shows causality test case 3, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 4}
shows causality test case 4, for which the \co{r1 == r2 == 1} result
is to be forbidden.
The herd7 tool finds this OOTA cycle, and flags it as such using \co{S8}.

@@

Listing~\ref{lst:Causality Test Case 5}
shows causality test case 5, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The herd7 tool finds this OOTA cycle, and flags it as such using \co{S8}.

@@

Listing~\ref{lst:Causality Test Case 6}
shows causality test case 6, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 7}
shows causality test case 7, for which the \co{r1 == r2 == r3 == 1}
result is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 8}
shows causality test case 8, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 9}
shows causality test case 9, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 9a}
shows causality test case 9a, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 10}
shows causality test case 10, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The herd7 tool nevertheless reports this result and does not flag it as
an OOTA cycle.

@@

>>>>

Listing~\ref{lst:Causality Test Case 1}
shows causality test case 1, for which the \co{r1 == r2 == 1} result
is to be allowed.
However, the \co{herd7} tool does not find this litmus test's cycle, presumably
because this tool does not do the deep inter-thread compiler analysis
required to find it.

@@

Listing~\ref{lst:Causality Test Case 2}
shows causality test case 2, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The \co{herd7} tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 3}
shows causality test case 3, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The \co{herd7} tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 4}
shows causality test case 4, for which the \co{r1 == r2 == 1} result
is to be forbidden.
The \co{herd7} tool finds this OOTA cycle, and flags it as such using \co{S8}.

@@

Listing~\ref{lst:Causality Test Case 5}
shows causality test case 5, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The \co{herd7} tool finds this OOTA cycle, and flags it as such using \co{S8}.

@@

Listing~\ref{lst:Causality Test Case 6}
shows causality test case 6, for which the \co{r1 == r2 == 1}
result is to be allowed.
The \co{herd7} tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 7}
shows causality test case 7, for which the \co{r1 == r2 == r3 == 1}
result is to be allowed.
The \co{herd7} tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 8}
shows causality test case 8, for which the \co{r1 == r2 == 1}
result is to be allowed.
The \co{herd7} tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 9}
shows causality test case 9, for which the \co{r1 == r2 == 1}
result is to be allowed.
The \co{herd7} tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 9a}
shows causality test case 9a, for which the \co{r1 == r2 == 1}
result is to be allowed.
The \co{herd7} tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 10}
shows causality test case 10, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The \co{herd7} tool nevertheless reports this result and does not flag it as
an OOTA cycle.

@@

\subsubsection{Causality Test Case 11}
\label{app:Causality Test Case 11}

Listing~\ref{lst:Causality Test Case 11}
shows causality test case 11, for which the \co{r1 == r2 == r3 == r4 == 1}
result is to be allowed.
The \co{herd7} tool reports this result and does not flag it as an OOTA cycle.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-11.litmus @@
\caption{Causality Test Case 11}
\label{lst:Causality Test Case 11}
\end{listing}

\subsubsection{Causality Test Case 12}
\label{app:Causality Test Case 12}

JMM Causality Test Case 12 uses arrays, which are not yet supported
by the \co{herd7} tool.

\subsubsection{Causality Test Case 13}
\label{app:Causality Test Case 13}

Listing~\ref{lst:Causality Test Case 13}
shows causality test case 13, for which the \co{r1 == r2 == 1}
result is to be forbidden.
The \co{herd7} tool nevertheless reports this result and does not flag it as
an OOTA cycle.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-13.litmus @@
\caption{Causality Test Case 13}
\label{lst:Causality Test Case 13}
\end{listing}

\subsubsection{Causality Test Case 14}
\label{app:Causality Test Case 14}

Listing~\ref{lst:Causality Test Case 14}
shows causality test case 14, for which the \co{r1 == r3 == 1 && r2 == 0}
result is to be forbidden.
The \co{herd7} tool does not report this result.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-14.litmus @@
\caption{Causality Test Case 14}
\label{lst:Causality Test Case 14}
\end{listing}

\subsubsection{Causality Test Case 15}
\label{app:Causality Test Case 15}

Listing~\ref{lst:Causality Test Case 15}
shows causality test case 15, for which the \co{r0 == r1 == r3 == 1 && r2 == 0}
result is to be forbidden.
The \co{herd7} tool does not report this result.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-15.litmus @@
\caption{Causality Test Case 15}
\label{lst:Causality Test Case 15}
\end{listing}

\subsubsection{Causality Test Case 16}
\label{app:Causality Test Case 16}

Listing~\ref{lst:Causality Test Case 16}
shows causality test case 16, for which the \co{r1 == 2 && r2 == 1}
result is to be allowed.
The \co{herd7} tool does not report this result, which is to be expected
given the differences between Java on the one hand and C and C++
on the other.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-16.litmus @@
\caption{Causality Test Case 16}
\label{lst:Causality Test Case 16}
\end{listing}

\subsubsection{Causality Test Case 17}
\label{app:Causality Test Case 17}

Listing~\ref{lst:Causality Test Case 17}
shows causality test case 17, for which the \co{r1 == r2 == r3 == 42}
result is to be allowed.
The \co{herd7} tool does not report this result, which is to be expected
given the differences between Java on the one hand and C and C++
on the other.
But note that the \co{herd7} tool correctly notes the presence of an
OOTA cycle with \co{S17}.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-17.litmus @@
\caption{Causality Test Case 17}
\label{lst:Causality Test Case 17}
\end{listing}

\subsubsection{Causality Test Case 18}
\label{app:Causality Test Case 18}

Listing~\ref{lst:Causality Test Case 18}
shows causality test case 18, for which the \co{r1 == r2 == r3 == 42}
result is to be allowed.
The \co{herd7} tool does not report this result, which is to be expected
given the differences between Java on the one hand and C and C++
on the other.
But note that the \co{herd7} tool correctly notes the presence of an
OOTA cycle with \co{S17}.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-18.litmus @@
\caption{Causality Test Case 18}
\label{lst:Causality Test Case 18}
\end{listing}

\subsubsection{Causality Test Case 19}
\label{app:Causality Test Case 19}

Listing~\ref{lst:Causality Test Case 19}
shows causality test case 19, for which the \co{r1 == r2 == r3 == 42}
result is to be allowed.
The \co{herd7} tool does not report this result, which is to be expected
given the differences between Java on the one hand and C and C++
on the other.
But note that the \co{herd7} tool correctly notes the presence of an
OOTA cycle with \co{S8}.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-19.litmus @@
\caption{Causality Test Case 19}
\label{lst:Causality Test Case 19}
\end{listing}

\subsubsection{Causality Test Case 20}
\label{app:Causality Test Case 20}

Listing~\ref{lst:Causality Test Case 20}
shows causality test case 20, for which the \co{r1 == r2 == r3 == 42}
result is to be allowed.
The \co{herd7} tool does not report this result, which is to be expected
given the differences between Java on the one hand and C and C++
on the other.
But note that the \co{herd7} tool correctly notes the presence of an
OOTA cycle with \co{S8}.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-20.litmus @@
\caption{Causality Test Case 20}
\label{lst:Causality Test Case 20}
\end{listing}
